Summary Tables

### 2019-05-03 summary_tables.Rmd
Fix trip prop by identifying unique trips and then using them as denominator

for(city in cities){

  df <- io[[city]]$trip_scen_sets
  df1 <- df %>% dplyr::filter(scenario == "Baseline") %>% group_by(trip_id, trip_mode, scenario)
  u_trips <- nrow(df1)
  td <- df %>% group_by(trip_id, trip_mode, scenario) %>% group_by(trip_mode, scenario) %>% summarise(p = round(dplyr::n() /  u_trips * 100, round_to)) %>% spread(key = trip_mode, value = p) %>% mutate(row_sums = rowSums(.[sapply(., is.numeric)], na.rm = TRUE))
  td[2:6, 1] <- rownames(scen_prop)
  td <- as.data.frame(t(td))
  print(kable(t(td), caption = paste("Trip proportion (%) by mode for ", city)))
  cat("\n")
}

>>>>

for(city in cities){
  df <- io[[city]]$trip_scen_sets
  u_trips <- df %>% dplyr::filter(scenario == "Baseline") %>% summarise(uid <- n_distinct(trip_id)) %>% as.numeric()
  td <- df %>% distinct(trip_id, scenario, .keep_all = T) %>% group_by(trip_mode, scenario) %>% summarise(p = round(dplyr::n() / u_trips * 100, 1)) %>% spread(key = trip_mode, value = p) %>% mutate(row_sums = rowSums(.[sapply(., is.numeric)], na.rm = TRUE))
  td <- as.data.frame(t(td))
  names(td) <- lapply(append('baseline', rownames(scen_prop)), as.character)
  td <- td[-1, ]
  print(kable(td, caption = paste("Trip proportion (%) by mode for ", city)))
  cat("\n")
}
